Derogations and Democratic Backsliding: Exploring the Pandemic's Effects on Civic Spaces

### 2021-03-16 analysis/index.Rmd
Initial commit

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

Title <- "Derogations and Democratic Backsliding: Exploring the Pandemic's Effects on Civic Spaces"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2021"
```

# `r Title`

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of International Affairs • Lewis & Clark College  
[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University

---

@@

>>>>

---
title: "Derogations and Democratic Backsliding: Exploring the Pandemic's Effects on Civic Spaces"
author: "Suparna Chaudhry and Andrew Heiss"
date: "`r format(Sys.time(), '%F')`"
# site: safesite::safesite
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

## Code

All the raw code and data for this paper is available in a [GitHub repository](https://github.com/andrewheiss/covid-derogations).
